Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-14 journal paper/content/sec-theory.tex
Minor fix.
Minor edits.

We characterize the inherent quality of an MAB algorithm in terms of its \emph{Bayesian Instantaneous Regret} (henceforth, \BIR), a standard notion from machine learning:
\begin{align}\label{eq:theory-BIR-defn}
\BIR_i(n) := \E\sbr{ n\cdot \max_{a\in A} \mu_a - \rew_i(n)}.
\end{align}
We are primarily interested in how \BIR scales with $n$: typically, how fast \BIR decreases with $n$. We treat $K$, the number of arms, as a constant unless specified otherwise. Intuitively, (much) better MAB algorithms tend to have a (much) smaller BIR, see Appendix~\ref{app:examples} for more background.

>>>>

We characterize the inherent quality of an MAB algorithm in terms of its \emph{Bayesian Instantaneous Regret} (henceforth, \BIR), a standard notion from machine learning:
\begin{align}\label{eq:theory-BIR-defn}
\BIR_i(n) := \E\sbr{ \max_{a\in A} \mu_a - \rew_i(n)}.
\end{align}
We are primarily interested in how fast \BIR decreases with $n$. (We treat the number of arms as a constant.) Intuitively, (much) better MAB algorithms tend to have a (much) smaller BIR, see Appendix~\ref{app:examples} for background.
